\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[spanish,english,polish]{babel}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[normalem]{ulem}
\usepackage{float}
\usepackage{indentfirst}
\usepackage{soul}
\usepackage[utf8]{inputenc}
\useunder{\uline}{\ul}{}
\begin{document}
\title{{\huge Lekcja 19} \\
{\large Coping with English language competition tasks}}
\author{Zbigniew Żołnierowicz}
\date{29.10.2019}
\maketitle
\section{Test E}
Uzupełnij tłumaczenia zdań na angielski, nie zmieniając niczego we fragmentach już przetłumaczonych
\begin{enumerate}
    \item \begin{itemize}
        \item Dla mnie najgorszą datą konferencji byłby 1 marca. Nawet 20 luty byłby trochę lepszy.
        \item For me {\bf the worst date of the} conference {\bf would be} 1 March. Even 20 February {\bf would be slightly better}.
    \end{itemize}
    \item \begin{itemize}
        \item Jeśli weźmiemy samochód Tatusia zamiast naszego, nie uwierzą nam.
        \item {\bf If we take} Daddy's car instead {\bf of ours, they won't believe} us.
    \end{itemize}
    \item \begin{itemize}
        \item Jako że dziewczęta wydają się być bardziej skłonne niż chłopcy do uczenia się języków, nie powinno być zadnych problemów ze znalezieniem kilku, które mogłyby pracować jako tłumaczki na obozie.
        \item As girls tend to be better language learners {\bf than boys, there shouldn't be any problems with finding a couple, that could work} as translators at the camp.
    \end{itemize}
    \item \begin{itemize}
        \item Musi trochę potrwać zanim słuchacze zorientują się [=\emph{REALISE}] jaka jest prawidłowa odpowiedź.
        \item It must take some time before {\bf they realise what the correct answer is}.
    \end{itemize}
    \item \begin{itemize}
        \item Jak szybko przyzwyczaił się pan do noszenia munduru w biurze?
        \item How quickly {\bf did you get used to wearing} a uniform in the office?
    \end{itemize}
    \item \begin{itemize}
        \item Proszę, nie przyjmujmy [=\emph{TAKE}] nowych członków do naszego chóru przed festiwalem! Jeśli poślemy tam tylko dobrze wyszklonych śpiewaków, mamy pewność zdobycia jednej z nagród.
        \item {\bf Please, let's not take on new members of} our choir before the festival. {\bf If we send only} the well-trained singers there, we are certain {\bf to win at least one of the awards}.
    \end{itemize}
    \item \begin{itemize}
        \item Robotnikom, którzy będą robili remont na Cowley Road, nie wolno tknąć starego dębu, o którym sądzi się, że ma 400 lat. Grzywna za zniszczenie go byłaby wyższa od rachunku za remont.
        \item The workers {\bf who will be carrying out} the repairs on Cowley Road {\bf must not touch} the old oak that {\bf is thought to be 400 years old}. The fine for damaging it {\bf would be higher than} the bill for the repair.
    \end{itemize}
\end{enumerate}
\section{Test F}
Wpisz w odpowiedniej formie czasowniki w nawiasach
\begin{enumerate}
    \item In the end I decided [tell + not] {\bf not to tell} my aunt about the incident. I can imagine what she [say] {\bf would say} about it: that I [be] {\bf was} cruel to my dog.
    \item No more than five deer [shoot] were shot in the area since guns with telescopic sights [forbid] {\bf were forbidden} by the Forestry Department.
    \item I am glad to say that the complaint we made aout the dirty beach seems [work] {\bf to be working:} at present the wastebins [empty] {\bf are emptied} every day and the sand [change] {\bf is changed} once a week.
    \item In this little book you will find safety regulations for all sorts of emergency, e.g.: when a gas pipe [damage] {\bf is damaged}, the firemen first [cut off] {\bf cut off} electricity supply and then [install] {\bf install} ventilators to drive out the leaked gas.
    \item I don't know why you were so upset; after all, when the divorce proceedings [start] {\bf started}, Peter and Sue [live + not] {\bf havent been living together} for at least two yars.
    \item Two weeks after the course [begin] {\bf had begun}, all the parents who [feel] {\bf felt} that the progress that their kids [make] {\bf were making} [be] {\bf was} too slow [invite] {\bf were invited} to contact the psychoogist. Not many of them did.
\end{enumerate}
\section{Test G}
Uzupełnij zdania komentujące treść zdań wprowadzających.
\begin{enumerate}
    \item \begin{itemize}
        \item We first carefully weighed the parcel and only then discovered that the manufacturer had put the eact weight on the label.
        \item We needn't {\bf have weighed the parcel} because its weight {\bf was put on the label}
    \end{itemize}
    \item \begin{itemize}
        \item ``How badly did it hurt when you touched the wire?'' asked the doctor.
        \item The first question that the doctor asked me was how {\bf badly it hurt when I touched the wire}. 
    \end{itemize}
    \item \begin{itemize}
        \item I'm afreaid that our protest will not be taken seriously as long as we only express our own opinions.
        \item I think our voices will not be heard if we only speak for {\bf ourselves}.
    \end{itemize}
    \item \begin{itemize}
        \item In the end I'll go to Copenhagen alone, as our Danish colleagues will be busy on Monday. I don't like it.
        \item I wish somebody {\bf went to Copenhagen with} me. 
    \end{itemize}
    \item \begin{itemize}
        \item Dad is sure that one day Cindy will be selected for the national team. He will celebrate this day with a botthe of French champagne.
        \item Daddy will open {\bf a bottle of French champagne on the} day {\bf Cindy is selected for the} national team.
    \end{itemize}
    \item \begin{itemize}
        \item ``How serious is your boss about the deadline?'' I asked Arthur after the meeting. ``I don't know', was the answer.
        \item When I spoke to Arthur after the meeting he said {\bf he wasn't aware of how serious his boss was about the deadline}.
    \end{itemize}
    \item \begin{itemize}
        \item Mr McCoy has no trace of a Scottish accent because his family left Scotland when he was two.
        \item If Mr McCoy {\bf didn't leave Scotland at the age of 2,} he {\bf would've ended up} with a Scottish accent.
    \end{itemize}
    \item \begin{itemize}
        \item ``But Daddy, can't Pam and I take a little sip of wine? Just to celebrate Granny's birthday!''\\``No, absolutely not.''
        \item I treat it as a matter of principle never {\bf to let} my children {\bf drink} alcohol.
    \end{itemize}
\end{enumerate}
\end{document}