\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[spanish,english,polish]{babel}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[normalem]{ulem}
\usepackage{float}
\usepackage{indentfirst}
\usepackage{soul}
\usepackage[utf8]{inputenc}
\useunder{\uline}{\ul}{}
\begin{document}
\title{{\huge Lekcja 22} \\
{\large Writing an informal email to a friend}}
\author{Zbigniew Żołnierowicz}
\date{12.11.2019}
\maketitle
\section{A new restaurant}
\emph{We've discovered a new restaurant in our neighborhood.}\\
There aren't that many interesting places you can go to close by to chow down on some grub.
You have your usual places, like McDonald's, Subway and KFC, so this little family-run restaurant was quite the surprise to see.
It's called ``La Parma'', and it serves italian food, such as pizza and spaghetti.
What drew me in was the discount for couples, where you need to only pay 75\% of the regular price, if you come with a significant other, so I went there with my girlfriend.

The place seemed pretty par for the course, so I ordered my usual pick for such a place - a pizza with mushrooms, ham and chicken.
It's really hard to make good pizza, especially with enough ingredients on it that you can't count them on the fingers of your hands,
so I was pleasantly surprised by the fact that, not only was the pizza full of ingredients, it was also delicious!
None of the ingredients overpowered the other, the chicken wasn't dry, which plagues so many other pizzerias and the cheese was tasty and stringy.

Of course, tasty food is half the story when talking about a restaurant, I must also talk about the service.
The servers were really worth the tip. They remembered my order correctly, asked if I wanted to order some appetisers or water and - lo and behold - even remembered my name!
Though that wasn't that hard, seeing as there were only 4 other people with me at the time.

Are there any good places to eat where you live? I'm particularly interested in the independent stuff with dishes from unusual countries, for example Georgian cuisine.

\emph{Looking forward to reading your comments.}
\end{document}