\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[spanish,english,polish]{babel}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[normalem]{ulem}
\usepackage{float}
\usepackage{indentfirst}
\usepackage{soul}
\usepackage[utf8]{inputenc}
\useunder{\uline}{\ul}{}
\begin{document}
\title{{\huge Lekcja 10} \\
{\large Unit 6 ``Journeys'' - review}}
\author{Zbigniew Żołnierowicz}
\date{24.09.2019}
\maketitle
\section{Workbook}
\subsection{Task 4 - Identify a grammar error in each sentence. Rewrite correct sentences in your notebook.}
\begin{enumerate}
    \item \begin{itemize}
        \item The longer the journey, the most satisfying your arrival.
        \item The longer the journey, the more satisfying your arrival.
    \end{itemize}
    \item \begin{itemize}
        \item The trip was as wonderful an experience I could have imagine.
        \item The trip was as wonderful an experience as I have imagined.
    \end{itemize}
    \item \begin{itemize}
        \item The train ride was more tiring that dull.
        \item The train ride was more tiring than dull.
    \end{itemize}
    \item \begin{itemize}
        \item It was so an exciting adventure that I couldn't calm down for days
        \item It was such an exciting adventure that I couldn't calm down for days
    \end{itemize}
    \item \begin{itemize}
        \item I'd say the water was fresh rather as cold.
        \item I'd say the water was fresh rather than cold.
    \end{itemize}
    \item \begin{itemize}
        \item The hotel was not so much posh than extravagant.
        \item The hotel was not so much posh as extravagant.
    \end{itemize}
\end{enumerate}
\subsection{Task 5}
Belgrade really is just \textbf{as amazing a} city as Berlin. There is \textbf{such a good} vibe on the streets that it's hard to believe the levels of poverty and unemployment which still blight much of Serbia. In fact, it's not so \textbf{much surprising} as astonishing given how war tore the area just over fifteen years ago. The budget-end accommodation may best be described as basic rather \textbf{than comfortable} but what you get for your money is not to be questioned. With more bars, caf\'es, restaurants and clubs than you could possibly visit in a week, my advice is: \textbf{the earlier} you start, the more you'll get to see and do. So, if you fancy seeing a city which,, for the moment at least, is \textbf{rather fresher} than clich\'ed, do yourself a favour and visit Belgrade before everyone finds out what they're missing.
\subsection{Task 6}
Sri Lanka has become my favourite holiday destination and I go there \st{every time} \textbf{whenever} I can. The country offers great value for money \st{even if your budget is limited} \textbf{however your budget is limited} and you can count on good weather \st{any} \textbf{whichever} time of year - summer or winter. \st{Any place} \textbf{Wherever} you go in Sri Lanka the people are friendly and welcoming. \st{It doesn't matter what} \textbf{no matter what} your interests are, you will find there is something for everyone and \st{it doesn't matter who} \textbf{whoever} thinks Sri Lanka lacks cultural depth - they are wrong: it actually has as many as eight World Heritage Sites. There's more to do here than in Thailand or Cambodia or \st{any other place} \textbf{wherever else}. Once you get there, you will ask yourself why on earth you didn't go before.
\subsection{Task 7}
\begin{enumerate}
    \item The more \textbf{expensive the hotel, the better} the facilities
    \item Certain behaviour may mistakenly \textbf{pass for bad manners} in some countries.
    \item I buy souvenirs \textbf{whenever I visit} places - which is quite often nowadays.
    \item We always had a cooked family meal \textbf{however exhausted we felt} at the end of the day.
    The \textbf{majority of children} decided to take the river boat trip
\end{enumerate}
\end{document}