\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[spanish,english,polish]{babel}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[normalem]{ulem}
\usepackage{float}
\usepackage{indentfirst}
\usepackage{soul}
\usepackage[utf8]{inputenc}
\useunder{\uline}{\ul}{}
\begin{document}
\title{{\huge Lekcja 13} \\
{\large Contemporary artist's career - reading comprehension}}
\author{Zbigniew Żołnierowicz}
\date{08.10.2019}
\maketitle
\section*{Test F}
\begin{enumerate}
    \item \begin{itemize}
        \item The kids will certainly refuse to sit still for an hour or so and you will have to make a portrait from a photo.
        \item Without having {\bf the kids sit still for} at least an hour, you can only order a portrait painted from a photograph
    \end{itemize}
    \item \begin{itemize}
        \item We don't know whether or not Diana's parents had told her of Mary. She never mentioned her twin sister in her poems.
        \item Diana {\bf either hadn't been told about} or {\bf hadn't acknowledged Mary's} existence. Either way she didn't seem to care.
    \end{itemize}
    \item \begin{itemize}
        \item Joe Alex was well known for his punctuality. His colleagues annot recall a single case of his coming late for work.
        \item Joe {\bf was known for his punctuality, it's} said {\bf that he has never came in late for work}.
    \end{itemize}
    \item \begin{itemize}
        \item A hundred litres of helium weighs 20 grams while the same volume of hydrogen weighs only 11 grams. But hydrogen burns too easily rto be used in a balloon.
        \item Although helium is almost {\bf twice as heavy as} hydrogen, it is much better for balloons because it doesn't burn.
    \end{itemize}
    \item \begin{itemize}
        \item Don't worry about th eweather. The hut is insulated against cold, but, of course, not against temperatures below the freezing point.
        \item Cold nights won't be {\bf a problem, unless the temperature} falls {\bf below the freezing point}.
    \end{itemize}
    \item \begin{itemize}
        \item Miranda: Why didn't anyone tell me admission was free on Fridays?
        \item Miranda wishes {\bf she was told about free admission on Fridays}.
    \end{itemize}
    \item \begin{itemize}
        \item Lenni's tragic death in a car crash may have been the cause of her parents' eventually divorcing.
        \item Lenni's death in a car crash may have caused her parents to fall {\bf apart}.
    \end{itemize}
    \pagebreak
    \item \begin{itemize}
        \item There was a police terminal at every gate. Fans with any negative records were banned from entry.
        \item Entry to the stadium was not allowed to those {\bf on whom the police} had intelligence suggesting they might make trouble
    \end{itemize}
    \section*{Test G}
    \begin{itemize}
        \item All the evidence {\bf shows} that after the Roman Empire {\bf had fallen}, Western Europeans {\bf had kept on} {\bf living} in much the same way as they always {\bf have been}, except that they no longer {\bf had to pay} taxes to Rome. And the Roman towns {\bf had fallen} into ruin, because they {\bf have never had} any function other than the military administration of the Empire.
        \item The kids are ecstatic about a real family weekend which we {\bf haven't had} in a while and which, weather {\bf permitted} we {\bf would spend} {\bf trekking} along the coast.
        \item He {\bf returned} to the country in 2001. All the media welcomed him as a hero and his presence {\bf swung} public opinion in favour of the war. (Although this {\bf is} debatable.) This greatly {\bf upsetted} him as he never {\bf had seeked} popularity, always {\bf shunning} the limelight.
        \item She admitted I {\bf had} every right to {\bf be upset} as I {\bf was promised} {\bf to be paid} much more and certainly {\bf did not expect} {\bf to be made} {\bf to behave} like an idiot.
        \item Well, if he {\bf was} aware of the danger and {\bf did} nothing {\bf to warn} the customers, which undoubtedly {\bf would've spared} some lives, he {\bf would've been brought} to justice now.
        \item I don't recall ever {\bf meeting} the man. But {\bf having attended} Fredonia between 1980 and 1982, I {\bf passed by} him many times in the campus without {\bf thinking} our paths {\bf would cross} so dramatically one day.
    \end{itemize}
\end{enumerate}
\end{document}