\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[spanish,english,polish]{babel}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[normalem]{ulem}
\usepackage{float}
\usepackage{indentfirst}
\usepackage{soul}
\usepackage[utf8]{inputenc}
\useunder{\uline}{\ul}{}
\begin{document}
\title{{\huge Lekcja 16} \\
{\large Phrases with ``if''}}
\author{Zbigniew Żołnierowicz}
\date{22.10.2019}
\maketitle
\section{Student's book}
\subsection{Task 1, page 129}
\begin{enumerate}
    \item \begin{itemize}
        \item He isn't a famous playwright, but he acts like someone who is. {\bf AS IF}
        \item He isn't a famous playwright, but he acts as if he was one.
    \end{itemize}
    \item \begin{itemize}
        \item We have a very small chance of getting tickets for Adele's concert. If we got them, we wouldn't be able to go anyway. {\bf EVEN}
        \item We have a very small chance of getting tickets for Adele's concert, and even if we got them, we wouldn't be able to go anyway.
    \end{itemize}
    \item \begin{itemize}
        \item If you are not sure, ask somebody who has already seen the play if it's worth seeing. {\bf DOUBT}
        \item If in doubt, ask somebody who has already seen the play if it's worth seeing.
    \end{itemize}
    \item \begin{itemize}
        \item Do you consider him a talented singer? And if you don't think he is a talented singer, why do you want to see him live in concert? {\bf NOT}
        \item Do you consider him a talented singer? If not, why do you want to see him live in concert? {\bf NOT}
    \end{itemize}
    \item \begin{itemize}
        \item I didn't find the plot of hisnew film very convincing. If it made any impression on me at all, it made me appreciate his previous works more. {\bf ANYTHING}
        \item I didn't find the plot of hisnew film very convincing. If anything, it made me appreciate his previous works more.
    \end{itemize}
    \item \begin{itemize}
        \item You look pale. Have you had a shock? {\bf AS THOUGH}
        \item You look pale, as though you had a shock.
    \end{itemize}
    \item \begin{itemize}
        \item Do you think that he is a good music journalist? And if you think he is a good music journalist, can you explain why? {\bf SO}
        \item Do you think that he is a good music journalist? If so, can you explain why?
    \end{itemize}
    \item \begin{itemize}
        \item British audiences rarely, if at all, give shows a standing ovation. {\bf EVER}
        \item British audiences rarely, if ever, give shows a standing ovation.
    \end{itemize}
    \item \begin{itemize}
        \item There is little or no possibility at all that the series will run for a few more seasons.
        \item There is litte possibility, if any, that the series will run for a few more seasons.
    \end{itemize}
\end{enumerate}
\end{document}