\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[spanish,english,polish]{babel}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[normalem]{ulem}
\usepackage{float}
\usepackage{indentfirst}
\usepackage{soul}
\useunder{\uline}{\ul}{}
\usepackage[utf8]{inputenc}
\begin{document}
\title{{\huge Lekcja 06} \\
{\large Words and phrases with ``ever''}}
\author{Zbigniew Żołnierowicz}
\date{16.09.2019}
\maketitle
\section*{Textbook}
\subsection*{Task 2}
\subsubsection*{Dialogue 1}
\begin{description}
    \item[Janet] Which seat do you want - the window or the aisle?
    \item[Ben] \textbf{Whichever}, I don't mind.
\end{description}
\subsubsection*{Dialogue 2}
\begin{description}
    \item[James] \textbf{However} did you manage to park in there? That space is tiny!
    \item[Marta] I don't really know!
\end{description}
\subsubsection*{Dialogue 3}
\begin{description}
    \item[Sandy] It's such a long journey. Is it really worth it, do you think? I mean \textbf{whatever} form of transport we choose, it's gonna take us at least ten hours. And it's so expensive!
    \item[Paula] No, it isn't actuallym not at the moment. Look, there's a great offer for this weekend! Come on, you know it's worth it!
    \item[Sandy] OK, \textbf{whatever} - book the flights then!
\end{description}
\subsection*{Task 4}
\begin{enumerate}
    \item \begin{description}
        \item[A:] What film would you like to see?
        \item[B:] \emph{I don't care which} / \textbf{Whichever}, I am good with anything.
    \end{description}
    \item \emph{In what kind of shop} / \textbf{Whereever} did you find that bike?!
    \item \begin{description}
        \item[A:] You're not going out tonight.
        \item[B:] \emph{I don't care!} / \textbf{Whatever!}
    \end{description}
    \item \emph{The person who} / \textbf{Whoever} did this is going to have to pay for the damages
\end{enumerate}
\subsection*{Task 6}
\begin{enumerate}
    \item There are \textbf{ever} increasing opportunities to travel. And this is set to contnue in the future!
    \item The world is getting ever-smaller. This has many positives and negatives.
    \item Speaking even a little of the local language is \textbf{ever} so useful.
    \item Travelling is the best experience \textbf{ever}.
    \item There are more opportunities than \textbf{ever} to learn from other cultures
    \item As \textbf{ever}, travelling to some parts of the world will always be restricted.
    \item Exploring your own country is \textbf{ever} such an educational experience.
\end{enumerate}
\section*{Textbook p. 126}
\subsection*{Task 1}
\begin{enumerate}
    \item \begin{itemize}
        \item Some people think mass tourism is a good thing but they are deluding themselves.
        \item \textbf{Whoever thinks mass tourism} has been entirely beneficial is deluding themselves.
    \end{itemize}
    \item \begin{itemize}
        \item It doesn't matter what tour operators claim, tourism rarely benefits the local community.
        \item \textbf{Whatever the tour operators claim}, tourism rarely benefits the local community.
    \end{itemize}
    \item \begin{itemize}
        \item Some people consider it good news that package holidays are becoming cheaper all the time.
        \item Some people consider it good news that package holidays \textbf{are getting ever so cheaper}.
    \end{itemize}
    \item \begin{itemize}
        \item No matter where tourists go, they cause land, food, water, housing and infrastructure prices to increase.
        \item \textbf{Wherever the tourists go}, they cause land, food, water, housing and infrastructure prices to increase.
    \end{itemize}
    \item \begin{itemize}
        \item No matter which form of transport tourists use to travel abroad, their collective carbon footprint is huge.
        \item \textbf{Whichever form of transport} tourists use to travel abroad, their collective carbon footprint is huge.
    \end{itemize}
    \item \begin{enumerate}
        \item Although we all love holidays in nature, we should remember that tourism can easily destroy it.
        \item \textbf{However much we love} holidays in nature, we should remember that tourism can easily destroy it.
    \end{enumerate}
    \pagebreak
    \item \begin{itemize}
        \item As always, many careless tourists left rubbish behind and damaged local flora.
        \item Many \textbf{tourists, as ever}, left rubbish behind and damaged local flora.
    \end{itemize}
    \item \begin{itemize}
        \item Even though it is a very difficult issue to tackle, we must think of alternatives to mass tourism.
        \item Even though it is \textbf{ever so difficult} to tackle, we must think of alternatives to mass tourism.
    \end{itemize}
    \item \begin{itemize}
        \item No matter how many dollars it generates in revenue, the current system of international tourism is unsustainable.
        \item \textbf{However many dollars it} generates in revenue, the current system of international tourism is unsustainable.
    \end{itemize}
    \item \begin{itemize}
        \item While it may take a long time, a way must be found to manage tourism before it destroys the environment.
        \item \textbf{However long it may take}, a way must be found to manage tourism before it destroys the environment.
    \end{itemize}
    \item \begin{itemize}
        \item The attitudes towards tourism and nature conservation are changing very slowly.
        \item The attitudes towards tourism and nature conservation \textbf{are changing ever so slowly}.
    \end{itemize}
    \item \begin{itemize}
        \item Tourism has an impact on local communities in europe, Asia or in any place.
        \item Tourism has an impact on local communities in \textbf{Europe, Asia or wherever else}.
    \end{itemize}
\end{enumerate}
\end{document}