\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[spanish,english,polish]{babel}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[normalem]{ulem}
\usepackage{float}
\usepackage{indentfirst}
\usepackage{soul}
\usepackage[utf8]{inputenc}
\useunder{\uline}{\ul}{}
\begin{document}
\title{{\huge Lekcja 15}}
\author{Zbigniew Żołnierowicz}
\date{15.10.2019}
\maketitle
\section{Test E}
\begin{enumerate}
    \item \begin{itemize}
        \item To, czego nam nie wolno robić jako dziennikarzom, to sprzyjać jednej ze stron w walce politycznej partii.
        \item {\tt What we must not to do as journalists is to} take sides in\\party politics.
    \end{itemize}
    \item \begin{itemize}
        \item Opłata pocztowa była tak duża, bo list był trzykrotnie cięższy od listu standardowego.
        \item The postage was so {\tt costly, because the letter was three\\times as heavy as a standard letter}.
    \end{itemize}
    \item \begin{itemize}
        \item Tamtego ranka na peronie nie wiedzieli, że przez prawie dwadzieścia lat mieli się nie zobaczyć.
        \item That morning on the platform they {\tt didn't know they wouldn't see each other for} nearly twenty years.
    \end{itemize}
    \item \begin{itemize}
        \item Obrazek, który najbardziej mi się podoba, to ten przedstawiający Mount Everest
        \item {\tt The picture that I like the most is the one displaying\\Mount Everest}
    \end{itemize}
    \item \begin{itemize}
        \item Film miał bardzo optymistyczne przesłanie, co, jak sądzę, było przyczyną, że ludziom tak się spodobał.
        \item The movie {\tt had a very positive message, which is,\\I presume,} why {\tt people liked it so much}
    \end{itemize}
    \item \begin{itemize}
        \item Co do mnie, nigdy nie używam słów, których nie chcę, by używały moje dzieci. Oczywiście to nie uchroni je przed podchwyceniem takich słów gdzie indziej.
        \item Personally, I {\tt don't use words I don't want my kids to use.\\Of course, that won't prevent them from picking up those\\words somewhere else.}
    \end{itemize}
    \item \begin{itemize}
        \item Dowiedzieliśmy się, że będziemy musieli poczekać 12 godzin na następny prom, bo nasz odpłynął dziesięć minut temu.
        \item We learnt {\tt that we're going to have to wait 12 hours for}\\another ferry {\tt as ours left 10 minutes ago}.
    \end{itemize}
\end{enumerate}
\pagebreak
\section{Test F}
\begin{enumerate}
    \item \begin{itemize}
        \item ``Why aren't there more movies like yours, Mr Gibson?'' \\ ``Well, next question, please.''
        \item When asked {\tt why there weren't more movies like his,}\\Mel Gibson just smiled and {\tt asked for the next question}.
    \end{itemize}
    \item \begin{itemize}
        \item Unit 301, formed as the latest special operations unit in the Army, is not as well known as its predecessors.
        \item Unit 301 {\tt is the least} known {\tt of} all special operations units in the army.
    \end{itemize}
    \item \begin{itemize}
        \item Safety is ensured by explosives experts who check every room in the building.
        \item The risk of a bombing attempt is minimized by {\tt a careful scan} by explosives experts.
    \end{itemize}
    \item \begin{itemize}
        \item ``I will not accept any homework assignments after the deadline'', says Dr Fromm. ``The only excuse is a doctor's certificate''
        \item {\tt Unless} a doctor's certificate {\tt is} presented, no late assignments {\tt will be accepted}.
    \end{itemize}
    \item \begin{itemize}
        \item ``FORTEX has no medical effect,'' concluded a committee of experts in its final report. A year later it was still used by many hospitals.
        \item Despite {\tt a committee of experts having} found FORTEX to lack {\tt any medical effect}, it was not withdrawn {\tt from many hospitals.}
    \end{itemize}
    \item \begin{itemize}
        \item According to the school discipline rules, a student who is caught with a knife may face expulsion from school.
        \item Possession of a knife is regarded as a serious offence which may result in {\tt expulsion}.
    \end{itemize}
    \item \begin{itemize}
        \item We have to reveal the scandal, but we fear that this is likely to cause panic in the market.
        \item The risk that the moment the scandal {\tt gets revealed}, there will be panic in the market is {\tt high}.
    \end{itemize}
    \item \begin{itemize}
        \item In this remote country, missionaries have to learn to work with no support from any individuals or institutions.
        \item In this remote country, missionaries have to learn to support\\{\tt themselves}.
    \end{itemize}
\end{enumerate}
\pagebreak
\section{Test G}
\begin{itemize}
    \item The next morning Col. Travis {\tt [report]} {\bf reported} that the river {\tt [rise]} {\bf has risen} two inches in an hour and {\tt [warn]} {\bf warned, that} if the rain {\tt [stop + not]} {\bf doesn't stop}, he {\tt [be]} {\bf will be} unable to build the bridge.
    \item The assumption is that by the time they {\tt [reach]} {\bf reach} the 6th grade, pupils {\tt [read]} {\bf will have read} enough books about nature to allow them to do their own research.
    \item The famous saying about there {\tt [be]} {\bf being} only two sure things in life, death and taxes, {\tt [attribute]} {\bf has been attributed} to many authors, including Benjamin Franklin. Today it {\tt [overuse + not]} {\bf is not overused}, as it {\tt [seem]} {\bf seems} {\tt [become]} {\bf to become} something of a clich\'e.
    \item The boys {\tt [saw]} {\bf had sawn} off a few alder branches that {\tt [hang]} {\bf hung} low over the beach, then {\tt [bind]} {\bf bound} them with wire into a raft. The work completed, they {\tt [hide]} {\bf hid} the raft in thick bushes and went home.
    \item The police searched the house a day after the incident. They {\tt [find]} {\bf found} no guns, no explosives, no fingerprints. What they {\tt [find]} {\bf found}, however, was an empty bullet case, {\tt [suggest]} {\bf suggeting} the bandits {\tt [hide]} {\bf have hidden} there. But this {\tt [be]} {\bf could've been} a coincidence, after all.
    \item Of course, we {\tt [go on]} {\bf went on} with our criticism of the school. But isn't it time we {\tt [lay]} {\bf laid} the issue to rest and {\tt [start]} {\bf started} {\tt [think]} {\bf to think} about it in a more positive way?
\end{itemize}
\section*{Rozprawka}
\begin{itemize}
    \item 200-250-280 słów
    \item nie powtarzać wyrazów
    \item użyć strony biernej
    \item Termin: wtorek
    \item Temat: W dzisiejszych czasach młodzież usiłuje wcześnie rozpocząć karierę w mediach społecznościowych, w branży muzycznej, bądź filmowej. Napisz rozprawkę, przedstawiającą wady i zalety tego zjawiska.
\end{itemize}
\end{document}