\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[spanish,english,polish]{babel}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[normalem]{ulem}
\usepackage{float}
\usepackage{indentfirst}
\usepackage{soul}
\useunder{\uline}{\ul}{}
\usepackage[utf8]{inputenc}
\begin{document}
\title{{\huge Lekcja 07} \\
{\large Travel experiences - listening comprehension}}
\author{Zbigniew Żołnierowicz}
\date{16.09.2019}
\maketitle
\section*{Textbook}
\subsection*{Task 3}
\begin{description}
    \item[Speaker 1] \begin{itemize}
        \item the pace of the itinerary/the unusual destination
        \item It was an exhilirating experience.
    \end{itemize}
    \item[Speaker 2] \begin{itemize}
        \item the freedom the trip allowed
        \item It had unforeseen drawbacks.
    \end{itemize}
    \item[Speaker 3] \begin{itemize}
        \item the need to please different people
        \item It was unexpectedly enjoyable.
    \end{itemize}
    \item[Speaker 4] \begin{itemize}
        \item the way the trip was financed
        \item It was a good way of relieving stress
    \end{itemize}
    \item[Speaker 5] \begin{itemize}
        \item the opportunity to meet new people
        \item It was worth the effort involved
    \end{itemize}
\end{description}
\subsection*{Task 5}
\begin{description}
    \item[play it by ear] improvise
    \item[take a dip] have a swim
    \item[get away from it all] escape your normal routine
    \item[get off the beaten track] go where few people go
    \item[travel on a shoestring] not spend much money on a trip
    \item[pinch yourself] convince yourself sth is not real
    \item[roll up] arrive
    \item[use your time wisely] not waste time
\end{description}
\subsection*{Task 6}
\begin{enumerate}
    \item I don't like to \textbf{play it by ear}. I like to have a plan.
    \item The most important thing on holiday is to \textbf{} and forget about life at home
    \item When I'm on holiday, I love \textbf{} first thing in the morning.
    \item I saw some wonderful things on my trip. I had to \textbf{} to make sure they were true.
    \item I don't like visiting tourist attractions. I like to \textbf{} and discover new things.
    \item I am very bad at \textbf{}. I never leave the hotel before noon.
    \item I never have a real summer vacation - I just \textbf{} at my friends' houses.
    \item I don't have a lot of money so I always have to \textbf{}
\end{enumerate}
\subsection*{Task 7}
\begin{enumerate}
    \item Bungee jumping is perfectly safe. \begin{itemize}
        \item Would you like to \emph{try it}?
        \item \textbf{Would you like to give it a go?}
    \end{itemize}
    \item \begin{itemize}
        \item Have you ever \emph{looked after} anyone's pet while they were on holiday?
        \item .
    \end{itemize}
    \item \begin{itemize}
        \item Last time you were shopping and had to choose between two brands, what was it that \emph{persuaded} you?
        \item .
    \end{itemize}
    \item \begin{itemize}
        \item If you were choosing holiday accommodation for your family, what would be the \emph{priority} for you?
    \end{itemize}
\end{enumerate}
\section*{Workbook}
\end{document}