\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[spanish,english,polish]{babel}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[normalem]{ulem}
\usepackage{float}
\usepackage{indentfirst}
\usepackage{soul}
\usepackage[utf8]{inputenc}
\useunder{\uline}{\ul}{}
\begin{document}
\title{{\huge Lekcja 22} \\
{\large }}
\author{Zbigniew Żołnierowicz}
\date{13.11.2019}
\maketitle
\section{Test 9}
\begin{enumerate}
    \item There are no problems with Dave. He seems {\bf to have been looked} after in a proper way.
    \item He knew {\bf too few Dutch words} to express how strongly he felt about this.
    \item Don't try to stop him. The sooner he {\bf resigns} the better. I certainly won't miss him.
    \item Hearing the sad news, she {\bf burst into tears}. I'm still upset to think about it.
    \item By the time I came here all the better jobs {\bf had been taken}.
    \item As for Tina, we can be quite sure she will not say a word, even if she {\bf is spoken to}.
    \item If I might say something, I'd suggest {\bf not telling} Adam about it.
    \item I didn't hear the voice but if the man {\bf was} Barbara's father, we'll be in trouble. You shouldn't have told her about our meeting.
    \item My daughter prefers {\bf shops which} sell top quality goods only.
    \item I don't know what they're waiting for. We've agreed to depart once they {\bf have finished}.
    \item I've just had a quarrel with your father whether {\bf to allo wyou and your friends to go} fishing.
    \item Buenos Aires Radio says {\bf there is to be} a twenty-four hour general strike in Argentina on Friday.
    \item ``Monica has just left. She's sorry about being absent last Monday. She had to babysit for a neighbour.'' \\
    ``It's OK but {\bf she ought have phoned}.''
    \item It's great! I've never seen {\bf such fantastic} architecture in my life.
    \item I can remember she {\bf has lain} the dining-room table with a white cloth to celebrate my return.
\end{enumerate}
\section{Test 57}
\begin{enumerate}
    \item \begin{itemize}
        \item Czy ktoś mógłby mi powiedzieć, o kim ona mówiła?
        \item Can anyone tell me, whom was she talking about?
    \end{itemize}
    \item \begin{itemize}
        \item Czy już się namyśliłeś? Nie każ nam czekać zbyt długo.
        \item Have you made up your mind? Don't make us wait for too long.
    \end{itemize}
    \item \begin{itemize}
        \item Tylko spojrzałem na niego i wiedziałem, że znowu pił.
        \item As soon as I laid my eyes on him I knew he had been drinking again.
    \end{itemize}
    \item \begin{itemize}
        \item To niezupełnie tak. Naukowiec, o którego teorii mówisz, nie mieszka w Cambridge. Od 10 lat mieszka w Stanach Zjednoczonych.
        \item That's not quite true. The scientist, whose theory you're talking about, doesn't live in Cambridge. He has been living in the United States for 10 years.
    \end{itemize}
    \item \begin{itemize}
        \item Bądź ostrożny. Nikt nie powinien wiedzieć, czy pojawisz się w sobotę czy w niedzielę.
        \item Be careful. No one should know, whether you will appear on Saturday or on Sunday.
    \end{itemize}
    \item \begin{itemize}
        \item Jestem pewien, że mecz bardzo by ci się podobał. Ale Albert grał trochę gorzej niż zwykle.
        \item I'm sure you'd like the match very much. But Albert had played slightly worse than usual.
    \end{itemize}
    \item \begin{itemize}
        \item Miałem powiedzieć, że się nie zgadzam, kiedy wszedł generał.
        \item I was about to say, that I disagree, when the general walked in.
    \end{itemize}
    \item \begin{itemize}
        \item Dlaczego myślisz, że on będzie musiał zgodzić się na wysłanie na Północ?
        \item What made you think that he'll have to agree on being sent to the North?
    \end{itemize}
    \item \begin{itemize}
        \item Oni nie muszą wiedzieć, dokąd idziecie. Nie powinniście w ogóle odpowiadać na ich pytania.
        \item They don't need to know, where you are going to. You shouldn't answer their questions at all.
    \end{itemize}
    \item \begin{itemize}
        \item Galeria, dla której przygotowuję tę wystawę, będzie musiała ubiegać się [{\bf=APPLY}] o dotację z Rady Miasta.
        \item The gallery, for which I'm preparing this exhibition, will have to apply for a subsidy from the City Council.
    \end{itemize}
    \item \begin{itemize}
        \item Wiem, że to smutne. Ale przyznajmy [{\bf=ADMIT}], że ani pan ani ja nie możemy wiele zrobić dla tych biedaków.
        \item I know it's sad. But we have to admit, that neither you nor I are able to do much for these poor souls.
    \end{itemize}
    \item \begin{itemize}
        \item Jeśli na jutrzejszym teście uda ci się [{\bf=MANAGE}] zrobić tak mało błędów jak dziś, z pewnością będziesz miał jeden z czołowych wyników
        \item If you manage to get as little errors as today on tomorrow's test, you'll definitely have one of the top scores.
    \end{itemize}
    \item \begin{itemize}
        \item Nie pytaj go, dokąd idzie. Zdaje się bardzo śpieszyć.
        \item Don't ask him, where he's going. He seems to be very much in a hurry.
    \end{itemize}
    \item \begin{itemize}
        \item Było dużo telefonów od rodziców naszych uczniów, po tym jak radio podało, że bandytę [{\bf=criminal}] widziano w pobliżu South End.
        \item There were a lot of calls from the parents of our students, after when the radio informed, that the criminal had been seen near South End.
    \end{itemize}
    \item \begin{itemize}
        \item Nawet jeśli zachowywał się trochę lepiej niż zwykle, był znacznie gorszy od pozostałych chłopaków.
        \item Even if he behaved himself a little bit better than usual, he still was much worse than the rest of the boys.
    \end{itemize}
\end{enumerate}
\section{Workbook, pg. 100-101}
\subsection{Task 5}
\begin{enumerate}
    \item \begin{itemize}
        \item Amy is very shy so she was speechless when she eventually met the singer. \textbf{NOT}
        \item If she weren't so shy, Amy {\bf would not have been} speechless when she eventually met the singer
    \end{itemize}
    \item \begin{itemize}
        \item If my sports teacher hadn't encouraged me, I would never have become a successful figure skater. {\bf BUT}
        \item {\bf But for my sports teacher's encouragement}, I would have never become a successful figure skater.
    \end{itemize}
    \item \begin{itemize}
        \item Normally, nobody is allowed backstage, but what would you say if we just went there after the play? {\bf WHAT}
        \item {\bf What if we went backstage} after the play, what would you say? I know that normally nobody is allowed there.
    \end{itemize}
    \item \begin{itemize}
        \item Helena's membership won't be renewed unless she pays her subscription within the next week, {\bf SHOULD}
        \item {\bf Should Helena's membership remain unpaid for} within the next week, her membership won't be renewed.
    \end{itemize}
    \item \begin{itemize}
        \item If you started learning the drums now, you would soon be able to perform during school events. {\bf WERE}
        \item {\bf If you were to start learning the drums now}, you would soon be able to perform during school events.
    \end{itemize}
    \item \begin{itemize}
        \item No tourist may enter unless they wear helmets. {\bf CONDITION}
        \item Tourists may enter {\bf on condition that they wear} helmets.
    \end{itemize}
\end{enumerate}
\end{document}