\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[spanish,english,polish]{babel}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[normalem]{ulem}
\usepackage{float}
\usepackage{indentfirst}
\usepackage{soul}
\useunder{\uline}{\ul}{}
\usepackage[utf8]{inputenc}
\begin{document}
\title{{\huge Lekcja 05} \\
{\large Advanced comparative structures}}
\author{Zbigniew Żołnierowicz}
\date{10.09.2019}
\maketitle
\section*{Textbook}
\subsection{Task 3}
\begin{description}
    \item[not as uncomfortable a journey as I thought] the journey by taxi from \\
    Cairo to Djoser
    \item[less and less awe-inspiring the closer I got] Giza pyramid
    \item[more disappointed than impressed] Mark's feelings on approaching Giza
    \item[such a magnificent sight] Djoser pyramid
    \item[awe-struck rather than merely impressed] Mark's feelings on seeing Djoser 
    \item[the more remote the place, the greater the impression] general feelings about less touristy places
    \item[more agricultural than residential] the function of Moray
    \item[such a dark night] the evening of their arrival
    \item[not so much excited as impatient] Mark's feelings about having to wait
\end{description}
\subsection{Task 5}
\begin{enumerate}
    \item I wans't so much \textbf{disappointed in Paris as} underwhelmed.
    \item Personally, I'd say Rome is \textbf{bohemian rather than conservative}.
    \item Truly unspoilt land is \textbf{becoming less and less} common.
    \item It was \textbf{such a noisy hostel that} I couldn't get any sleep.
    \item Prague wasn't as \textbf{romantic a place as} I was expecting.
    \item Poland is still \textbf{more agricultural than} urban.
    \item The more you travel, \textbf{the more cultured you} become.
    \item Berlin wasn't \textbf{such an expensive city as} I thought it would be.
\end{enumerate}
\subsection{Task 6}
\begin{enumerate}
    \item \begin{itemize}
        \item Vienna is the most delightful city I've ever visited.
        \item \textbf{AS}
        \item I've never visited as \textbf{delightful a city as} Vienna.
    \end{itemize}
    \item \begin{itemize}
        \item It's getting increasingly hard to find a cheap B\&B.
        \item \textbf{AND}
        \item It's getting \textbf{harder and harder} to find a cheap B\&B.
    \end{itemize}
    \item \begin{itemize}
        \item People suffer greater homesickness the further they travel from home
        \item \textbf{MORE}
        \item The further away you travel from home, \textbf{the more homesick} you get.
    \end{itemize}
    \item \begin{itemize}
        \item She described the landscape as being more surreal than picturesque.
        \item \textbf{RATHER}
        \item She described the landscape as being \textbf{surreal rather than picturesque}.
    \end{itemize}
    \item \begin{itemize}
        \item We decided not to stay in the hotel because it was so expensive
        \item \textbf{SUCH}
        \item It was \textbf{such an expensive hotel} that we decided not to stay there
    \end{itemize}
    \item \begin{itemize}
        \item The itinerary was less daunting than it at first looked.
        \item \textbf{NOT}
        \item It \textbf{wasn't as daunting} an itinerary as it at first looked.
    \end{itemize}
    \item \begin{itemize}
        \item The water was so cold it was unbearable 
        \item \textbf{THAT}
        \item It was \textbf{such cold water that} it was unbearable
    \end{itemize}
    \item \begin{itemize}
        \item If you ask me, I'd say the sea is green not blue.
        \item \textbf{THAN}
        \item In my opinion, the sea \textbf{is more green than blue}.
    \end{itemize}
\end{enumerate}
\section*{Workbook}
\subsection{Task 2}
\begin{enumerate}
    \item The journey was \st{tougher} \textbf{more tough} than dangerous
    \item Lisa and Donald are such \st{a} friendly people that I'd love to settle down in their neighborhood.
    \item \st{As} \textbf{The} steeper the slope, \st{as} \textbf{the} more difficult it is to ski.
    \item When Jack and his co-climbers looked at the surrounding peaks, they were overwhelmed rather \st{then}\textbf{than} thrilled
    \item On reaching their destination, the tourists weren't so much exhausted \st{than} \textbf{as} irritated.
\end{enumerate}
\subsection{Task 3}
\begin{enumerate}
    \item \begin{itemize}
        \item[A:] And? Going to Mexico alone wasn't a good idea, was it? \textbf{SUCH}
        \item[B:] Well, it wasn't \textbf{such a bad idea}, either. I had a chance to brush up on my Spanish.
    \end{itemize}
    \item \begin{itemize}
        \item[A:] I believe London is a more enchanting city than Edinburgh. \textbf{CITY}
        \item[B:] That's unfair! Edinburgh is \textbf{as enchanting a city} as London!
    \end{itemize}
    \item \begin{itemize}
        \item[A:] Our tour guide seems rather distracted, don't you think? \textbf{MUCH}
        \item[B:] I wouldn't say that. She isn't \textbf{as much distracted as} disorganised.
    \end{itemize}
    \item \begin{itemize}
        \item[A:] I reckon the package tour was a fantastic offer. \textbf{SO}
        \item[B:] On the contrary! It wasn't \textbf{so fantastic an} offer as I had previously thought.
    \end{itemize}
\end{enumerate}
\subsection{Task 4}
\begin{enumerate}
    \item such easy access
    \item not as much pleasure as
    \item as big an adventure as
    \item rarer and rarer
\end{enumerate}
\end{document}