\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[spanish,english,polish]{babel}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[normalem]{ulem}
\usepackage{float}
\usepackage{indentfirst}
\usepackage{soul}
\usepackage[utf8]{inputenc}
\useunder{\uline}{\ul}{}
\begin{document}
\title{{\huge Lekcja 20} \\
{\large Expressing various attitudes to readevelopment plan}}
\author{Zbigniew Żołnierowicz}
\date{04.11.2019}
\maketitle
\section{Student's Book}
\subsection{Task 5}
\begin{enumerate}
    \item {\bf Local regeneration} is beneficial because it brings money into poorer neighboourhoods.
    \item {\bf Legal battles} often occur when people can't agree about the best way for the city to grow.
    \item Building {\bf cultural institutions} like concert halls is good for both the arts and business.
    \item {\bf Property developers} usually make a lot of money when the economy is doing well.
    \item It woould be good to have a {\bf creative hub} near where I live so that artists could meet.
    \item There are all these {\bf pop-up shops} in my town - every month the businesses change.
    \item Sometimes even at {\bf public consultation} the opinions of local residents aren't taken into account.
    \item I don't feel that major {\bf redevelopment plans} are always the best way forward. Sometimes it is good to preserve the past.
    \item There is no point in protesting once governments or big businesses have made decisions and something is a {\bf done deal}
\end{enumerate}
\end{document}