\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[spanish,english,polish]{babel}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[normalem]{ulem}
\usepackage{float}
\usepackage{indentfirst}
\usepackage{soul}
\usepackage[utf8]{inputenc}
\useunder{\uline}{\ul}{}
\begin{document}
\title{{\huge Lekcja 16} \\
{\large Key word transformation}}
\author{Zbigniew Żołnierowicz}
\date{16.10.2019}
\maketitle
\begin{enumerate}
    \item \begin{itemize}
        \item Znam bardzo niewielu ludzi, którzy mogliby sobie pozwolić na tak kosztowne meble. Nie ma wśród nich żadnego z moich braci.
        \item I know very few people, that could afford such expensive furniture. None of my brothers are such people.
    \end{itemize}
    \item \begin{itemize}
        \item Nie będę się dziwił, jeśli mężczyzna, którego szukacie od dwóch tygodni, wkrótce pojawi się na konferencji prasowej w Miami.
        \item I won't be surprised, if the man you've been searching for for 2 weeks soon appears on a press conference in Miami.
    \end{itemize}
    \item \begin{itemize}
        \item Im głośniej mówisz, tym one stają się bardziej hałaśliwe.
        \item The louder you speak, the more noisy they get.
    \end{itemize}
    \item \begin{itemize}
        \item Gdyby ona spodziewała się odesłania do domu, nie byłaby taka wystraszona [={\bf scared}]
        \item Were she expecting to be sent home, she wouldn't be so scared.
    \end{itemize}
    \item \begin{itemize}
        \item Najwyższy czas, żeby ktoś porozmawiał z nim poważnie. Żaden nauczyciel nie zrobi tego lepiej od bliskiego przyjaciela.
        \item It's high time someone talked to him seriously. No teacher can do it better than a close friend.        \item 
    \end{itemize}
    \item \begin{itemize}
        \item Jak można by ustalić [={\bf find out}], ile będzie referatów pierwszego dnia rano?
        \item How could one find out how many essays will be there on the first day in the morning?
    \end{itemize}
    \item \begin{itemize}
        \item Nie zapłacę, dopóki ona mi dokładnie nie powie, za co chce tyle pieniędzy.
        \item I won't pay, until she tells me exactly why she wants all that money.
    \end{itemize}
    \item \begin{itemize}
        \item Było późno ale jestem pewien, że Mary zdążyła [={\bf catch}] jednak na pociąg. Ona zawsze zdąża.
        \item It was late, but I'm sure Mary caught the train either way. She always catches one.
    \end{itemize}
    \item \begin{itemize}
        \item Nie musi pan rzucać palenia, ale nie wolno panu palić 40 papierosów dziennie.
        \item You don't have to stop smoking, but you musn't smoke 40 smokes a day.
    \end{itemize}
    \item \begin{itemize}
        \item Dowiedziałem się o jego decyzji tydzień temu, a ciągle jeszcze o niej myślę.
        \item I heard of his decision a week ago, and I'm still thinking about it now.
    \end{itemize}
    \item \begin{itemize}
        \item Wiedziałem że wszystko będzie dobrze. Ale nie mogłem opanować [={\bf help}] zdenerwowania.
        \item I knew everything was going to be alright. But I couldn't help myself being agitated.
    \end{itemize}
    \item \begin{itemize}
        \item Szkoda, że nie kupiłeś tego zegarka. Mogłeś go dać ojcu na urodziny.
        \item It's a shame you didn't buy that watch. You could've gifted it to your dad for his birthday.
    \end{itemize}
    \item \begin{itemize}
        \item Może będziesz musiał przestać się z nią widywać przez jakiś czas. Ale nie martw się.
        \item You may have to stop seeing with her for a while. But don't worry.
    \end{itemize}
    \item \begin{itemize}
        \item Prawdę mówiąc, nie lubię klasycznego tańca; ale nie mógłbym jutro iść do opery, nawet gdybym lubił.
        \item To tell the truth, I don't like classical dance; but I couldn't go to the opera tomorrow, even if I did.
    \end{itemize}
    \item \begin{itemize}
        \item Bądź cierpliwszy. Jeśli się za bardzo rozzłościsz, nie będziesz mógł wygłosić przemówienia.
        \item Be more patient. If you get too agitated, you won't be able to present your speech.
    \end{itemize}
\end{enumerate}
\end{document}