\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[spanish,english,polish]{babel}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[normalem]{ulem}
\usepackage{float}
\usepackage{indentfirst}
\usepackage{soul}
\usepackage[utf8]{inputenc}
\useunder{\uline}{\ul}{}
\begin{document}
\title{{\huge Lekcja 24} \\
{\large }}
\author{Zbigniew Żołnierowicz}
\date{12.11.2019}
\maketitle
\section{Test 1}
\begin{enumerate}
    \item He frowned, unable to hide his \emph{an{\bf n}oyance} at the interruption. ``Can't you see I'm busy?''
    \item Before the auction, many people will no doubt \emph{inq{\bf u}ire} about the paintings put on sale. So you have to be ready to answer many phones.
    \item Speeding is a driving \emph{of{\bf f}ense} subject to a fine. It is not a crime, though.
    \item Dr Rayton, who \_\_r\_\_\_\_\_ was ambassador to Moscow, is now a secretary of state at the Foreign Office.
    \item Before humans turned to farming, they subsisted as hunters and \emph{ga{\bf t}herers}.
    \item The Queen was highly cultured and \emph{en{\bf t}ertained} her guests with music and poetry reading.
    \item All the fresh and frozen \_\_\_v\_\_\_\_\_\_ for the cruise have already been loaded onto the ship.
    \item At the first meeting after the elections, Mr Jay Kabinda was elected \emph{chai{\bf r}person} of the Committee.
    \item Nathaniel Greene was oe of George Washington's most gifted and trusted generals, next in line of \emph{co{\bf m}mand} of the Continental Army after Washingthon himself.
    \item The best known example of a successful \_\_c\_\_\_ was the Trojan Horse.
    \item The anglers were hidden in the greenery. We only saw several fishing \emph{nets} along the river bank.
    \item The cupboard was too wide to go through the door. It had to be turned \emph{si{\bf d}eways}.
    \item In rough seas the \emph{lo{\bf w}ering} of lifeboats from the sinking ship can be a problem.
    \item With demand for healthy food rising, the economic \emph{ou{\bf t}look} for ecological farming is very good.
    \item The cleaning lady was careful not to touch the papers and books \emph{pi{\bf l}ed} up on his desk.
    \item It all went \emph{\_\_\_\_\_{\bf d}\_\_\_\_} well with not the slightest problem.
    \item There are four or five routes to take, but \emph{whi{\bf c}hever} option you choose, you will have to pay at least 200 bucks.
    \item We were impressed on how much she \emph{ac{\bf c}omplished} in such a short time, from learning English to pursuing a college degree and only being in New York for two years.
    \item A sawed-off shotgun is a gun with its \emph{ba{\bf r}ell} sawed off for greater close-range damage.
    \item The \emph{\_\_{\bf a}\_\_\_\_\_} is a straight line between two sides of a circle, passing through the centre.
    \item The energy yield of the first atom bomb was \emph{eq{\bf u}ivalent} to 16 thousand tons of dynamite.
    \item Trains for carrying goods are called \emph{\_\_{\bf e}\_\_\_\_} trains.
    \item The good news is that Madden is to be \emph{re{\bf l}eased} from the hospital tomorrow.
    \item The Quran is the \emph{\_\_{\bf c}\_\_\_} book of Islam.
    \item Women's right to ote became an important \emph{\_\_{\bf s}\_\_} only in the $20^{th}$ century.
    \item We will not be able to offer food and \emph{be{\bf d}ding} to so many guests.
    \item \emph{\_\_\_{\bf m}\_\_\_} music is written for small groups of musicians.
    \item Cars are cheap here. A car of a \emph{co{\bf m}parable} size would cost twice as much abroad.
    \item The official Guinness World Rcord has been broken by 28 girls in the UK, who managed to \emph{\_\_{\bf u}\_\_\_\_} themselves into a new-shape Mini.
    \item The \emph{su{\bf s}pect} is being interrogated and will no doubt be arrested.
\end{enumerate}
\end{document}