\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[spanish,english,polish]{babel}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[normalem]{ulem}
\usepackage{float}
\usepackage{indentfirst}
\usepackage{soul}
\usepackage[utf8]{inputenc}
\useunder{\uline}{\ul}{}
\begin{document}
\title{{\huge Lekcja 16} \\
{\large ---}}
\author{Zbigniew Żołnierowicz}
\date{21.10.2019}
\maketitle
\section{Test E}
\subsection*{Uzupełnij tłumaczenia zdań na angielski, nie zmieniając niczego we fragmentach już przetłumaczonych}
\begin{enumerate}
    \item \begin{itemize}
        \item Kiedy spytałem ich obecną sytuację klubu, powiedzieli, że wcale nie wygląda ona źle.
        \item When I asked {\bf about the current situation of the club, they said that it wasn't bad at} all.
    \end{itemize}
    \item \begin{itemize}
        \item Problem z moim mężem polega na tym, że on ani nie chce, żebym ja podjęła pracę ani am nie próbuje znaleźć lepszej pracy.
        \item The problem with my husband is that {\bf neither does he want me to get a job, nor is he trying to find a better one for himself.}
    \end{itemize}
    \item \begin{itemize}
        \item Potrafią spędzać godziny kłócąc się [={\bf ARGUE}] o najmniej ważne szczegóły projektu. Co gorsza, niczego się nie uczą na swoich wcześniejszych błędach.
        \item They can spend hours {\bf arguing about the least important details of} the project. What is {\bf worse}, they {\bf learn nothing from their past} errors.
    \end{itemize}
    \item \begin{itemize}
        \item Na godzinę przed meczem biuro Prezydenta nie potrafiło nam powiedzieć, czy Prezydent przybędzie na stadion czy nie.
        \item An hour before the match the President's office {\bf couldn't tell us whether or not the President would come} to the stadium.
    \end{itemize}
    \item \begin{itemize}
        \item Kiedy próbuję sobie wyobrazić [={\bf IMAGINE}] kobietę, od której dostajemy te paczki, widzę ją jako gospodynię domową w średnim wieku z silnym akcentem niemieckim.
        \item When I {\bf imagine the woman, from whom we get these packages, I see her as a middleaged} housewife with a strong German accent.
    \end{itemize}
    \item \begin{itemize}
        \item W szkole podstawowym ulubionym chwytem mojej nauczycielki przedmiotów ścisłych było pokazanie nam kawałka drewna i zapytanie, czy wiemy, co to za drewno i gdzie zostało ścięte.
        \item In primary school my science teacher's favourite trick {\bf was to show us} a piece of wood and ask {\bf us what that wood is and where it was cut down}.
    \end{itemize}
    \item \begin{itemize}
        \item Sprawienie, żeby Tina zmieniła zdanie może nie być łatwym zadaniem. Gdy ona raz zadecyduje [={\bf DECIDE}], że nie wolnojej czegoś zrobić, to koniec i nie jesteś w stanie tego zmienić.
        \item {\bf Making Tina change} her mind {\bf might not be} an easy task. Once {\bf she decides she isn't allowed to do} a thing, it's finished and you {\bf can't do anything to change that}.
    \end{itemize}
\end{enumerate}
\section{Test F}
\subsection*{Uzupełnij zdania wyrażające w inny sposób treść zdań wprowadzających.}
\begin{enumerate}
    \item \begin{itemize}
        \item Take onepill on Monday, then another one on Wednesday, then the next on Friday, and so on...
        \item The doctor has told me to take {\bf one pill every second} day.
    \end{itemize}
    \item \begin{itemize}
        \item The second reading should eliminate all the errors from the script. That's the theory.
        \item Theoritically {\bf there should be no} errors in the script after the second reading.
    \end{itemize}
    \item \begin{itemize}
        \item Sally is almost sure the woman she saw in Dr Lang's car was not his wife. If she is right we may hear of yet another divorce soon.
        \item If the woman in Dr Lang's car {\bf wasn't} his wife, the Langs' marriage {\bf will end} in divorce. 
    \end{itemize}
    \item \begin{itemize}
        \item ``Do you speak French, Mr Lee?''\\``No, I don't. Neither do my brothers.''
        \item {\bf Neither Mr Lee nor any of the} Lee brothers speaks French.
    \end{itemize}
    \item \begin{itemize}
        \item Some ten years ago you left politics for a career in business. Do you ever regret it?
        \item Do you ever wish you {\bf hadn't left politics for a career in business?}
    \end{itemize}
    \item \begin{itemize}
        \item Tina's knee seems to be healing quite nicely and she will soon return to the team. Of course, the surgeon who has operated on her will have to see it first.
        \item Tina {\bf won't be returning to the team} until the surgeon {\bf who has operated on her sees it first.}
    \end{itemize}
    \item \begin{itemize}
        \item Don't tell me Jimmy had lunch at the canteen. He is just finishing the fifth sandwich.
        \item Jimmy {\bf was} so hungry on his return from school that he {\bf had lunch} at the canteen.
    \end{itemize}
    \item \begin{itemize}
        \item If Bob Oller had been present at the meeting, our lawyers would have asked him some difficult questions about his role in the scandal.
        \item Bob Oller chose to be absent from the meeting, thus avoiding {\bf being asked} difficult questions by our lawyers
    \end{itemize}
\end{enumerate}
\end{document}