\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[spanish,english,polish]{babel}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[normalem]{ulem}
\usepackage{float}
\usepackage{indentfirst}
\usepackage{soul}
\usepackage[utf8]{inputenc}
\useunder{\uline}{\ul}{}
\begin{document}
\title{{\huge Lekcja 12} \\
{\large Advanced vocabulary practice}}
\author{Zbigniew Żołnierowicz}
\date{24.09.2019}
\maketitle
\begin{description}
    \item[a juxtaposition] \begin{itemize}
        \item comparison of two things, one of which is dissimilar to the other
        \item ``The Hitchhiker's Guide to the Galaxy'' is a clever juxtaposition of wacky humor and philosophical questions about the meaning of life.
    \end{itemize}
    \item[point-blank] \begin{itemize}
        \item close range
        \item He shot at him at close range
    \end{itemize}
    \item[to gush] \begin{itemize}
        \item to talk excitedly about something, for fluid to come out of a hole in the ground in a violent manner
        \item He gushed about his new job
        \item The geiser gushes out
    \end{itemize}
    \item[ablaze] \begin{itemize}
        \item on fire
        \item Someone set the barn ablaze.
    \end{itemize}
    \item[to amass] \begin{itemize}
        \item to collect a large amount of something for a long time
        \item He amassed a lot of currency.
    \end{itemize}
    \item[pancreas] \begin{itemize}
        \item part of the digestive system responsivble for the production of insulin
        \item If you have diabetes, that means your pancreas is not working correctly.
    \end{itemize}
    \item[to rappel] \begin{itemize}
        \item to go down a mountain using a rappel line
        \item Six SWAT operators rappelled from the roof to the windows.
    \end{itemize}
    \item[a fern] \begin{itemize}
        \item a kind of plant that blossoms only once a year
        \item My mom has a couple of ferns that she takes care of every day.
    \end{itemize}
    \item[lackluster] \begin{itemize}
        \item lacking in substance
        \item He found his response lackluster.
    \end{itemize}
    \item[flabbergasted] \begin{itemize}
        \item surprised, astonished
        \item He was flabbergasted at what has transpired.
    \end{itemize}
    \item[to subside] \begin{itemize}
        \item to reduce in amount
        \item The symptoms have subsided
    \end{itemize}
    \item[to rebuff] \begin{itemize}
        \item to reject something in an ungracious manner
        \item He rebuffed his job offer, as he has found a more favourable position elsewhere.
    \end{itemize}
    \item[metastasis] \begin{itemize}
        \item spread of cancer to a different part of the host's body
        \item The cancer has metastasized to his lungs, killing him overnight.
    \end{itemize}
    \item[to tarnish] \begin{itemize}
        \item to make something less valuable or respected
        \item He tarnished his reputation by leaking his private e-mails.
    \end{itemize}
    \item[to pout] \begin{itemize}
        \item to push one's lips forward as an expression of annoyance
        \item Timmy pouted, because he couldn't take his favourite toy with him to school.
    \end{itemize}
    \item[innocuous] \begin{itemize}
        \item harmless
        \item Poisonous mushrooms seem innocuous at first.
    \end{itemize}
    \item[conifers] \begin{itemize}
        \item a type of tree with pinecones and needle-like leaves
        \item The nearby forest is filled with conifers.
    \end{itemize}
    \item[to disparage] \begin{itemize}
        \item to perceive something as having little value
        \item His actions always have a hidden purpose - to disparage his opponents.
    \end{itemize}
    \item[numb] \begin{itemize}
        \item lacking feeling
        \item Because of the hipothermia, his fingers went numb.
    \end{itemize}
    \item[clandestine] \begin{itemize}
        \item kept secret
        \item The details are to be clandestine.
    \end{itemize}
    \item[amiable] \begin{itemize}
        \item friendly
        \item He has a very amiable appearance.
    \end{itemize}
    \item[to cajole] \begin{itemize}
        \item to convince someone using flattery
        \item His promotion was thanks to him cajoling his boss.
    \end{itemize}
    \item[to decry] \begin{itemize}
        \item to condemn
        \item Great Britain and France decried the actions of Nazi Germany but initially, they did nothing about it.
    \end{itemize}
    \item[to renounce] \begin{itemize}
        \item to declare one's abandonment of something
        \item King Henry VIII renounced his country's main religion in favour of anglicanism.
    \end{itemize}
    \item[objective] \begin{itemize}
        \item goal
        \item His main objective was to take over the chairman seat.
    \end{itemize}
    \item[a boulder] \begin{itemize}
        \item a large rock
        \item Chris Redfield saved everyone by punching a boulder really hard.
    \end{itemize}
    \item[to respawn] \begin{itemize}
        \item to be reborn in a videogame
        \item I had to respawn because of his stupid tactics!
    \end{itemize}
    \item[to reciprocate] \begin{itemize}
        \item to return a favour
        \item He reciprocated his kindness with money.
    \end{itemize}
    \item[vague] \begin{itemize}
        \item description of something lacking in substance
        \item His recollection of the events was incredibly vague.
    \end{itemize}
    \item[unmitigated] \begin{itemize}
        \item something that hasn't been stopped
        \item If climate change is left unmitigated, we'll face global extinction in the next few generations.
    \end{itemize}
    \item[heiress] \begin{itemize}
        \item a woman that is to inherit something from her family
        \item She was a heiress to the throne.
    \end{itemize}
    \item[promiscuity] \begin{itemize}
        \item the characteristic of having many sexual relations
        \item Incels think women are full of promiscuity.
    \end{itemize}
    \item[laborious] \begin{itemize}
        \item taking a lot of time and work
    \end{itemize}
    \item[gruesome] \begin{itemize}
        \item disgusting
    \end{itemize}
    \item[to sow] \begin{itemize}
        \item to put seeds in the ground
    \end{itemize}
    \item[to begrudge] \begin{itemize}
        \item to envy
    \end{itemize}
    \item[avowed] \begin{itemize}
        \item stated publically
    \end{itemize}
    \item[to swing by] \begin{itemize}
        \item to go somewhere
    \end{itemize}
    \item[helter-skelter] \begin{itemize}
        \item in confusion
    \end{itemize}
\end{description}
\end{document}