\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[spanish,english,polish]{babel}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[normalem]{ulem}
\usepackage{float}
\usepackage{indentfirst}
\usepackage{soul}
\usepackage[utf8]{inputenc}
\useunder{\uline}{\ul}{}
\begin{document}
\title{{\huge Lekcja 26} \\
{\large Passive reporting structures}}
\author{Zbigniew Żołnierowicz}
\date{07.01.2020}
\maketitle
\section{Student's book}
\subsection{Task 6}
\begin{enumerate}
    \item Spending too much time watching a screen is generally thought \emph{to be} bad for you.
    \item Facebook is believed \emph{to have passed} its peak and teens are turning to other social media.
    \item More and more YouTube stars are said \emph{to have made} millions with their channels.
    \item Bethany Mota is estimated \emph{to have earned} a fortune in the last five years.
    \item YouTube is reported \emph{to have} more than one billion users
    \item The number of people watching her channel was reported \emph{to have been rising} for years.
\end{enumerate}
\section{Workbook}
\section{Task 2}
\begin{itemize}
    \item They believe that Facebook has changed their life.
    \item Facebook \emph{is believed to have changed} their life.
\end{itemize}
\begin{enumerate}
    \item \begin{itemize}
        \item Newspapers report that some participants of amateur talent shows aren't quite as amateur as TV stations would have us believe.
        \item Some participants of amateur talent shows \emph{are reported to be not} quite as amateur as TV stations would have us believe. 
    \end{itemize}
    \item \begin{itemize}
        \item At last month's conference many presenters feared that a large number of teenagers had grown so attached to the reality of social media that it was impossible for them to cut the cord.
        \item At last month's conference a large number of teenagers \emph{are feared to had grown} so attached to the reality of social media that it was impossible for them to cut the cord.
    \end{itemize}
    \item \begin{itemize}
        \item Some parents have pointed out that the new school rules weren't discussed with them in any way.
        \item The new rules \emph{are pointed out to not have been} discussed with parents in any way.
    \end{itemize}
    \item \begin{itemize}
        \item Last Friday they alleged that may viral YouTube videos were hoaxes.
        \item Last Friday many viral YouTube videos \emph{are alleged to have been} hoaxes.
    \end{itemize}
    \item \begin{itemize}
        \item Specialists agree that seeking validation online in the form of retweets and likes is exacerbating our desire to be accepted.
        \item Seeking validation in the form of retweets and likes \emph{is agreed to be exacerbating} our desire to be accepted.
    \end{itemize}
\end{enumerate}
\section{Task 3}
\begin{itemize}
    \item It \emph{is said that the term `life hack' was coined} in 2004 by technology journalist Danny O'Brien during the O'Reilly Emerging Technology Conference in San Diego, California.
    \item The term `life hack' \emph{is said to have been coined} in 2004 by technology journalist Danny O'Brien during the O'Reilly Emerging Technology Conference in San Diego, California.
\end{itemize}
\begin{enumerate}
    \item \begin{itemize}
        \item Back then it \emph{was understood that the phrase described} the shortcuts IT specialists used to complete their work.
        \item Back then the phrase \emph{was understood to describe} the shortcuts IT specialists used to complete their work.
    \end{itemize}
\end{enumerate}
\end{document}