\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[spanish,english,polish]{babel}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[normalem]{ulem}
\usepackage{float}
\usepackage{indentfirst}
\usepackage{soul}
\usepackage[utf8]{inputenc}
\setlength{\parskip}{1em}
\useunder{\uline}{\ul}{}
\begin{document}
\title{{\huge Lekcja 29} \\
{\large Unit 8 ``Text me!'' - review}}
\author{Zbigniew Żołnierowicz}
\date{20.01.2020}
\maketitle
\subsection{Task 7}
When it comes to new technology, it's not easy to know whose opinion to trust and what can truly be considered as a \emph{reliable} source of information.
The idea that mobile phones caused brain cancer, for example, was an early \emph{assertion} that, despite plenty of media fearmongering, never really gained much traction with eiher the avid phone buying public or experts in the medical world.
Another common \emph{misconception} is that microwave ovens cook food from teh inside out. I found out last week that it's simply not true!
Where do we get such ideas from and why is nothing seemingly \emph{straightforward} with the introduction of new technology and our understanding of it?
The media are regularly the first to \emph{disclose} such information in their role of reporting dangers in feigned public interest. Newspapers, however, have long been regarded as a \emph{trustworthy} source of actual fact.
Unfortunately with the internet spreading hearsay much more \emph{extensively} ad with greater speed, it has become even harder to tell \emph{trivial} word of mouth from valuable knowledge of the increasing hi-tech world around us.
One thing's for sure - don't \emph{underestimate} our ability to contrive untruths.
\subsection{Task 8}
\begin{enumerate}
    \item \begin{itemize}
        \item I'm not sure whether I should buy a new laptop or a tablet
        \item MINDS
        \item I'm \emph{in two minds} as to whether I should buy a new laptop or a tablet.
    \end{itemize}
    \item \begin{itemize}
        \item I make sure that I check my email every day.
        \item BASIS
        \item I make sure that I check my email \emph{on a daily basis}.
    \end{itemize}
    \item \begin{itemize}
        \item The report stated that a great many people have lost confidence in Internet privacy.
        \item REPORTED
        \item A great many people are \emph{reported to have lost} confidence in Internet privacy.
    \end{itemize}
    \item \begin{itemize}
        \item They say that increasing numbers of politicians are using blogs to gather support.
        \item TO
        \item Increasing numbers of politicians \emph{are said to be using} blogs to gather support.
    \end{itemize}
    \item \begin{itemize}
        \item My health is starting to suffer as a result of spending hours in front of a computer.
        \item TOLL
        \item Spending ours in front of the computer \emph{is taking a toll} on my health.
    \end{itemize}
    \item \begin{itemize}
        \item The markets report that music streaming sites are doubling in value.
        \item Music streaming sites are said to be doubling in value.
    \end{itemize}
\end{enumerate}
\end{document}