\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[spanish,english,polish]{babel}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[normalem]{ulem}
\usepackage{float}
\usepackage{indentfirst}
\usepackage{soul}
\usepackage[utf8]{inputenc}
\setlength{\parskip}{1em}
\useunder{\uline}{\ul}{}
\begin{document}
\title{{\huge Lekcja 28} \\
{\large Writing a formal letter in repsonse to a particular situation}}
\author{Zbigniew Żołnierowicz}
\date{17.01.2020}
\maketitle
Dear Mr. Generic of the Upper Fictionford City Council

Us residents of our town, believe that its infrastructure is unsuitable for anyone other than pedestrians or motorized folk.
While many of us do use cars, trucks or motorcycles, we are concerned about the pollution Upper Fictionford is producing - and we believe that the \textbf{pertinent} point to limiting it is to introduce more cycling paths.

Research has shown that an average journey by car is between 8 and 10 miles, which means an increase in the amount of CO$_2$ from our cars, while that distance could easily be travelled with a bicycle.
We also \textbf{take issue with} the mayor's recent decision to ban biking in our town park, \textbf{thus} taking a stance against an \textbf{increasing number} of citizens, where biking is fast becoming a healthy \textbf{aspect} of their lives.

In comparison, the neighbouring town of Little Chipping has built \textbf{untold amounts} of cycle pathways.
Should we not follow suit? Above all, \textbf{on a daily basis}, many cyclists get into accidents, because they are forced to use the main roads of our town, full of reckless drivers.
The City Council should have \textbf{vested interest} in assuring the safety and well-being of the common citizen, not necessarily one that has a motorized vehicle and it should embrace the so-called \emph{``Green Revolution''}

Yours sincerely,

Firstname Lastnameski,
Upper Fictionford Neighborhood Association.
\end{document}