\documentclass[a4paper]{article}
\usepackage{fancyhdr}
\usepackage{mathptmx}
\usepackage{microtype}
\usepackage{setspace}
\usepackage{lipsum}
\usepackage[T1]{fontenc}
\usepackage[spanish,english,polish]{babel}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[normalem]{ulem}
\usepackage{float}
\usepackage{indentfirst}
\usepackage{soul}
\usepackage[utf8]{inputenc}
\useunder{\uline}{\ul}{}
\begin{document}
\title{Young enterpreneurs}
\author{Zbigniew Żołnierowicz}
\maketitle
\section{Introduction}
Nowadays, young adults start their careers off early. They become social media influencers, music composers and independent film directors. Is this phenomenon an opportunity to earn a lot early in life, or is this golden goose merely an ugly duckling?
\section{A new way of learning, working and teaching}
Why is this occuring now, one might wonder? Of course, this is due to the wondrous invention of one Tim Berners-Lee: The Internet. You no longer need expensive degrees to get a decent job, the only thing you need is a phone or a laptop. There is an overabundance of tutorials, presentations and online lessons from the likes of Coursetro, Udemy or Pluralsight that are very affordable, even without prior work.

Furthermore, thanks to software like Slack, Github and other collaboration tools, a new type of employment was born. Nowadays, one does not even have to come in to work. Instead, we can work from anywhere in the world - remotely.
\section{A new level of competition}
With the decentralization of workplaces comes the globalized job market. One's work can always be outsourced to some business in a second world country, like India.

``But creative works will always have vacancies!'' one might think. However, how many new musicians appear on the top charts monthly? Not that many. The same happens in the movie industry. Tons of aspiring directors fail to push themselves forward, because there is just too many of them.
\section{Conclusion}
With the advent of communication development and lifestyle change, one might be tempted to drop their job and chase their dreams to revolutionize the world. Although we need to keep both feet on the ground and realize, that there is a reason, why the entertainment industry has not changed much in recent years.
\end{document}