\documentclass{article}
\usepackage[T1]{fontenc}
\usepackage[spanish,english,polish]{babel}
\usepackage[utf8]{inputenc}
\begin{document}
\title{{\huge Lekcja 24} \\
{\large Advanced vocabulary practice}}
\author{Zbigniew Żołnierowicz}
\date{02.04.2019}
\maketitle
\section{Side A}
\subsection{Translate into Polish}
\begin{description}
    \item[perfunctory] powierzchowny
    \item[hideous] ohydny
    \item[a scourge] zmora, plaga
    \item[to bolster] wzmocnić, podeprzeć
    \item[to glad-hand] pokazywać sztuczną wylewność
    \item[the endorsement] poparcie
    \item[to embezzle] defraudować
    \item[to chirp] ćwierkać, świergotać
    \item[to gasp] wzdechnąć w szoku
    \item[folly] głupota
    \item[to yearn] pragnąć
    \item[callous] bezduszny
    \item[to coerce] zmuszać
    \item[maroon] kasztanowy
    \item[a crooner] śpiewak
    \item[meticulous] skrupulatny do przesady, pedantyczny
    \item[the misdemeanor] wykroczenie (niżej niż crime)
    \item[to gore] ubodnąć (np.\@ byk)
    \item[to bestow] powierzyć
    \item[impeccable] nienaganny
\end{description}
\subsection{Translate into English}
\begin{description}
    \item[świerszcz] cricket
    \item[lniany] flaxen
    \item[czapla] heron
    \item[nienasycony] insatiable
    \item[parafianin] parishioner
    \item[parafia] parishion
\end{description}
\subsection{Kolokacje}
\begin{enumerate}
    \item He has such a perfunctory view of the world.
    \item He's hideous!
    \item The scourge of communism.
    \item He bolstered his claims.
    \item Politicians glad-hand their potential voters.
    \item Politicians want to get the endorsement of a majority.
    \item A politician was caught embezzling government funds.
    \item Birds are chirping.
    \item I was so shocked I gasped.
    \item Everything you did was a folly.
    \item I yearn for power.
    \item Politicians might be smiling but actually they're callous.
    \item He coerced her into dropping the charges.
    \item I'm selling a maroon sofa.
    \item I heard a crooner singing.
    \item A work-to-rule protest is being overly meticulous.
    \item His minor misdemeanor left his criminal record permanently stained.
    \item A bull gored me when I visited my grandparents.
    \item The lady of the lake bestowed the Excalibur upon me.
    \item That's some impeccable logic.
    \item I caught a cricket in a jar.
    \item I saw flour in flaxen bags.
    \item I went birdwatching with my dad and we saw some herons.
    \item I have an insatiable lust for hamburgers.
    \item Parishioners were walking out of the church.
\end{enumerate}
\end{document}