\documentclass{article}

\begin{document}

\title{Lekcja 21 --- Using various gerund structures}
\author{Zbigniew Żołnierowicz}
\date{12.03.2019}
\maketitle

\section{Page 124}

\subsection{Ex. 1}

\begin{enumerate}
  \item Have you ever {\tt considered taking} a year off work?
  \item In our company {\tt being a salesperson} involves travelling around the country.
  \item Tom's mother can't {\tt have imagined him working} in the medical field.
  \item On {\tt internship offering}, you are expected to contact the company as soon as possible and confirm your acceptance or rejection of the offer.
  \item When olivia started working here, she had {\tt difficulty getting} to grips with our database
  \item I apologised for {\tt not finishing} the project before the deadline.
\end{enumerate}

\subsection{Ex. 2}
\begin{enumerate}
  \item Our new intern is very young but {\tt he resents being treated} like a child.
  \item There's {\tt no point in sending off} your CV to this company because you don't have the right qualifications.
  \item They complained {\tt about not having} any training options.
  \item {\tt Being dressed smartly makes} a better impression at a job interview.
  \item {\tt With most skilled jobs depending} on technical knowledge, it's vital to acquire it at school.
  \item {\tt Not knowing} our company was on the verge of going bust, I didn't even think of looking for another job.
\end{enumerate}
\section{Homework, page 70}
\subsection{Ex. 1}
\begin{enumerate}
  \item {\tt Being} young and single, Jake didn't say no to the relocation to a different city.
  \item By mid spring, he'll have been {\tt interning} for us for a year.
  \item It's always worth {\tt checking} the details of any contract before you sign it.
  \item That man {\tt talking} to our head teacher is a famous enterpreneur and former student.
  \item Many employees admit to {\tt pretending} to be byst when their boss is looking.
  \item It's {\tt fascinating} to imagine where Mark Zuckerberg might be working now if he hadn't dropped out of Harvard.
\end{enumerate}

\subsection{Ex. 2}
Nancy Rica Schiff, an American photographer, is keen on {\tt bringing} some of the world's oddest professions to people's attention. Would you ever consider {\tt taking} such jobs as dog food tester, dinosaur duster or golf ball diver? No? Apparently some people out there have succeeded {\tt in} pursuing a career in these strange occupations. {\tt By} travelling around the USA for fifteen years, Nancy was tracking down professionals with unique jobs, from the person who dresses Barbie dolls for a living, a gumbuster whose job involves {\tt getting} rid of chewing gum marks from the streets, to knife-thrower's assistant, to mention just few. Miss Schiff claims she will never grow tired {\tt of} spotting occupations with a twist of humour, her favourite {\tt being} that of professional mermaid. So next time you fancy {\tt leaving} your job, you might want to refer to her art for inspiration.

\subsection{Ex. 3}
\begin{enumerate}
  \item {\tt Not having} any kind of formal training before, seriously they'd give me that job
  \item {\tt Having been dismissed} unfairly, my mum decided to go to court to fight for her rights.
  \item Don't tell anyone, but your brother was seen {\tt being reprimanded} by his boss in the restaurant today.
  \item Some students complained about {\tt not being sent} any information regarding the scholarship.
\end{enumerate}

\subsection{Ex. 4}
\begin{enumerate}
  \item The trainee waiter insisted {\tt on being given} weekly wages in advance.
  \item My new employer insisted {\tt on giving him} the references from my previous boss.
  \item Phil's Maths teacher doesn't approve {\tt of being called} a `slave driver' behind his back.
  \item Zoe's friends don't approve {\tt of her calling}
\end{enumerate}

\subsection{Ex. 5}
\begin{enumerate}
  \item {\tt On being given} a day off, Bess went on a shopping spree with her best friend.
  \item {\tt There's no point in asking} him for a pay rise.
  \item Many enterpreneurs complain that they {\tt are having difficulty getting} enough qualified staff.
  \item {\tt With more and more people leaving} the country, soon we'll experience a serious shortage of staff.
  \item {\tt It's no good talking} to her about promoting you now.
\end{enumerate}


\subsection{Ex. 6}
\begin{enumerate}
  \item {\tt Not being able to find} a job for one year, he was entitled to unemployment benefit.
  \item His partner doesn't {\tt approve of him accepting} that new job in the capital.
  \item {\tt Having been made redundant} so suddenly, Mark's parents hadn't prepared any contingency plan.
  \item {\tt On being told the news}, Fiona immediately called her parents for advice.
  \item Fifteen years in his profession and Arthur still {\tt has difficulty getting used} to night shifts.
  \item {\tt With her job getting} too stressful, Ella decided to take a year off and travel.
\end{enumerate}
\end{document}
% vim:set spelllang=pl:
