\documentclass{article}
\usepackage[T1]{fontenc}
\usepackage[english,polish]{babel}
\usepackage[utf8]{inputenc}
\begin{document}
\title{{\huge Lekcja 22} \\
{\large Job interview techniques --- listening comprehension}}
\author{Zbigniew Żołnierowicz}
\date{21.03.2019}
\maketitle
\section{Student's book}
\subsection{Page 58}
\subsubsection{Task 5}

\begin{enumerate}
    \item \emph{willing} --- willingness
    \item \emph{adaptable} --- adaptablility
    \item \emph{keen} --- keenness
    \item \emph{resourceful} --- resourcefulness
    \item \emph{self-assured} --- self-assurance
    \item \emph{persistent} --- persistence
    \item \emph{authentic} --- authenticity
    \item \emph{sincere} --- sincerity
    \item \emph{humble} --- humility
\end{enumerate}
\subsubsection{Task 6}
\begin{enumerate}
    \item He didn't give up when he failed and expressed a {\tt willingness} to take the test again.
    \item He showed great {\tt resourcefulness} and fount out almost everything about the job.
    \item Everyone appreciated her {\tt sincerity}. She never came across as fake or phony.
    \item Her boss liked her {\tt adaptablility} - how she could work in many different fields.
    \item She showed real {\tt persistence} and after seemingly endless interviews, finally got the job she wanted.
    \item Having {\tt self-assurance} and believing that you can succeed is important in work.
    \item She is incapable of admitting she is wrong - she has a complete lack of {\tt humility}.
    \item It's always better to say what you feel - {\tt sincerity} is the greatest of virtues.
    \item My teacher told me he liked the enthusiasm and {\tt keenness} to learn.
\end{enumerate}
\end{document}